Tree establishment in models of forest dynamics: a key priority for further research

### 2023-04-26 manuscript/manuscriptRW.Rmd
mainly I added oxford commas in mansucript

Tree establishment is a key process in forest dynamics, particularly in
the context of forest resilience and climate change. Models are pivotal
for assessing long term (i.e., decadal to centennial) forest dynamics,
and they have been in use for more than 50 years. However, an assessment
of their ability to accurately represent tree establishment is lacking.
We assess how well current models capture the overall abundance, species
composition and mortality of tree establishment.

@@

Despite considerable mismatches between simulation results and data in
some instances, it is remarkable that most of the models capture the
essential features of the highly complex process of tree establishment,
while not having been parameterized with such data. We conclude that in
spite of all the uncertainties, much can be gained by evaluating and
refining model establishment processes. This has the potential to render
long-term projections of forest dynamics under changing environmental
conditions much more robust.

>>>>

Tree establishment is a key process in forest dynamics, particularly in
the context of forest resilience and climate change. Models are pivotal
for assessing long term (i.e., decadal to centennial) forest dynamics,
and they have been in use for more than 50 years. However, an assessment
of their ability to accurately represent tree establishment is lacking.
We assess how well current models capture the overall abundance, species
composition, and mortality of tree establishment.

@@

Despite considerable mismatches between simulation results and data in
some instances, it is remarkable that most of the models capture the
essential features of the highly complex process of tree establishment,
while not having been parameterized with such data. We conclude that in
spite of all the uncertainties, much can be gained by evaluating and
refining model establishment processes. This has the potential to render
long-term projections of forest dynamics under changing environmental
conditions that are much more robust.
